\pkg{casebase}: An Alternative Framework For Survival Analysis

### 2020-02-06 analysis/paper/paper.tex
add discussion of flexible sampling

In Hanley \& Miettinen \citeyearpar{hanley2009fitting}, the authors
suggest sampling the base series \emph{uniformly} from the study base.
In terms of Poisson processes, this sampling strategy corresponds
essentially to a time-homogeneous Poisson process with intensity equal
to \(b/B\), where \(b\) is the number of sampled observations in the
base series, and \(B\) is the total population-time for the study base.
More complex examples are also available; see for example Saarela \&
Arjas \citeyearpar{saarela2015non}, where the probabilities of the
sampling mechanism are proportional to the cardiovascular disease event
rate given by the Framingham score.

@@

This report was generated on 2020-02-06 13:51:22 using the following
computational environment and dependencies:

@@

\begin{CodeOutput}
#> Local:    intro /home/turgeonm/Documents/git_repos/cbpaper
#> Head:     [92cad64] 2020-02-05: add intro and edit some of the sections
\end{CodeOutput}
\end{CodeChunk}

>>>>

In Hanley \& Miettinen \citeyearpar{hanley2009fitting}, the authors
suggest sampling the base series \emph{uniformly} from the study base.
In terms of Poisson processes, this sampling strategy corresponds
essentially to a time-homogeneous Poisson process with intensity equal
to \(b/B\), where \(b\) is the number of sampled observations in the
base series, and \(B\) is the total population-time for the study base.
More complex examples are also available; see for example Saarela \&
Arjas \citeyearpar{saarela2015non}, where the probabilities of the
sampling mechanism are proportional to the cardiovascular disease event
rate given by the Framingham score. With this sampling mechanism,
Saarela \& Arjas are able to increase the efficiency of their
estimators, when compared to uniform sampling.

@@

This report was generated on 2020-02-07 10:31:46 using the following
computational environment and dependencies:

@@

\begin{CodeOutput}
#> Local:    intro /home/turgeonm/Documents/git_repos/cbpaper
#> Head:     [d5e7d09] 2020-02-07: add discussion of flexible sampling
\end{CodeOutput}
\end{CodeChunk}
